A Large-scale Study of Polymorphism in R

### 2019-03-28 notebooks/paper_results_section.Rmd
updated counts in paper after controlling for failed traces, will push data separately later

I think something funky is happening.
We should have matrix types, maybe I forgot.
Dealing with that now:
```{r}
# NOTE matrix stuff moved up, oopsie
```

Top sig time.
```{r}
# poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
# poly_type_args <- poly_type_args[order(-poly_type_args$count),] # sort by count
# poly_type_args$perc <- round(poly_type_args$count/sum(poly_type_args$count) * 100, 2)
```

Print top 10.
```{r}
# format_df_for_print(poly_type_args[1:10,]) -> put_me
# put_me
# xtable(put_me) %>% print(include.rownames=F)
```

```{r}
# sigs_df_vec <- get_fun_sigs_matching_pred_from_lopkg(los, pred=does_df_have_X_types, types_to_find=c("matrix", "vector/real"), strict=T)
```

>>>>

Get the biggest signature.
```{r}
big <- get_biggest_function(los, metric=size_of_signature_type)

# it's %>%
```

### 2019-03-28 paper/main.tex
updated counts in paper after controlling for failed traces, will push data separately later

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsFGTS}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 784K & 85.28 \\ 
  Monomorphic in Type & 836K & 90.91 \\ 
  Monomorphic in Class & 831K & 90.31 \\ 
  Monomorphic in Attribute Pattern & 830K & 90.25 \\ 
  Total Seen & 920K & --- \\ 
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in the FGTS.}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:10:46 2019
\begin{table}[ht]
\label{tab:funcountsFGTS}
\centering
\begin{tabular}{lrr}
  \hline
 Function Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 143K & 65.80 \\ 
  Monomorphic in Type & 167K & 76.84 \\ 
  Monomorphic in Class & 163K & 75.13 \\ 
  Monomorphic in Attribute Pattern & 161K & 74.31 \\ 
  Total Seen & 217K & --- \\ 
   \hline
\end{tabular}
\caption{Account of {\it function} polymorphism in the FGTS.}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 21:27:37 2019
\begin{table}[ht]
\label{tab:toppolyFDTS}
\centering
\begin{tabular}{lrr}
  \hline
 Polymorphic Type Signature & \# Occurrences & \% of Total Polymorphism \\ 
  \hline
  vector/double, vector/integer & 7677 & 9.18 \\ 
  scalar/double, scalar/integer & 7194 & 8.61 \\ 
  matrix, vector/double & 5354 & 6.40 \\ 
  NULL, scalar/character & 2333 & 2.79 \\ 
  list$<$any$>$, list$<$double$>$ & 2224 & 2.66 \\ 
  data.frame, matrix & 2115 & 2.53 \\ 
  NULL, scalar/double & 2066 & 2.47 \\ 
  NULL, vector/double & 2042 & 2.44 \\ 
  list$<$any$>$, list$<$list$>$ & 1426 & 1.71 \\ 
  NULL, vector/character & 1385 & 1.66 \\ 
     \hline
\end{tabular}
\caption{Top polymorphic argument signatures in the FDTS.}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 785K & 85.38 \\ 
  Monomorphic in Type & 871K & 94.65 \\ 
%  Monomorphic in Class & 831K & 90.31 \\ 
%  Monomorphic in Attribute Pattern & 830K & 90.25 \\ 
  Total Seen & 920K & --- \\ 
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in the NEW TYPE SYSTEM.}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:10:46 2019
\begin{table}[ht]
\label{tab:funcountsWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
 Function Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 143K & 65.95 \\ 
  Monomorphic in Type & 184K & 84.778 \\
%  Monomorphic in Class & 163K & 75.13 \\ 
%  Monomorphic in Attribute Pattern & 161K & 74.31 \\ 
  Total Seen & 217K & --- \\ 
   \hline
\end{tabular}
\caption{Account of {\it function} polymorphism in the NEW TYPE SYSTEM.}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Mar 26 17:46:45 2019
\begin{table}[ht]
\label{tab:toppolyWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
Polymorphic Type Signature & \# Occurrences & \% of Total Polymorphism \\ 
  \hline
  matrix, vector/real & 6307 & 12.82 \\ 
  list$<$any$>$, list$<$real$>$ & 2792 & 5.68 \\ 
  vector/character, vector/real & 2719 & 5.53 \\ 
  scalar/character, scalar/real & 2536 & 5.16 \\ 
  data.frame, matrix & 2163 & 4.40 \\ 
  list$<$any$>$, list$<$list$>$ & 1492 & 3.03 \\ 
  list$<$any$>$, list$<$character$>$ & 1217 & 2.47 \\ 
  data.frame, vector/real & 1025 & 2.08 \\ 
  scalar/logical, scalar/real & 917 & 1.86 \\ 
  scalar/character, vector/real & 844 & 1.72 \\ 
   \hline
\end{tabular}
\caption{Top 10 argument signatures in the NEW TYPE SYSTEM.}
\end{table}

>>>>

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsFGTS}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 780K & 85.36 \\ 
  Monomorphic in Type & 832K & 91.03 \\ 
  Monomorphic in Class & 827K & 90.41 \\ 
  Monomorphic in Attribute Pattern & 825K & 90.27 \\ 
  Total Seen & 914K & --- \\ 
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in the FGTS.}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:10:46 2019
\begin{table}[ht]
\label{tab:funcountsFGTS}
\centering
\begin{tabular}{lrr}
  \hline
 Function Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 143K & 65.87 \\ 
  Monomorphic in Type & 167K & 76.95 \\ 
  Monomorphic in Class & 163K & 75.21 \\ 
  Monomorphic in Attribute Pattern & 161K & 74.37 \\ 
  Total Seen & 216K & --- \\ 
   \hline
\end{tabular}
\caption{Account of {\it function} polymorphism in the FGTS.}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 21:27:37 2019
\begin{table}[ht]
\label{tab:toppolyFDTS}
\centering
\begin{tabular}{lrr}
  \hline
 Polymorphic Type Signature & \# Occurrences & \% of Total Polymorphism \\ 
  \hline
  vector/double, vector/integer & 8228 & 10.03 \\ 
  scalar/double, scalar/integer & 7190 & 8.76 \\ 
  matrix, vector/double & 5362 & 6.54 \\ 
  NULL, scalar/character & 2308 & 2.81 \\ 
  list$<$any$>$, list$<$double$>$ & 2220 & 2.71 \\ 
  data.frame, matrix & 2115 & 2.58 \\ 
  NULL, scalar/double & 2064 & 2.52 \\ 
  NULL, vector/double & 2041 & 2.49 \\ 
  list$<$any$>$, list$<$list$>$ & 1420 & 1.73 \\ 
  NULL, vector/character & 1374 & 1.67 \\ 
     \hline
\end{tabular}
\caption{Top polymorphic argument signatures in the FDTS.}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 781K & 85.46 \\
  Monomorphic in Type & 867K & 94.78 \\
%  Monomorphic in Class & 831K & 90.31 \\ 
%  Monomorphic in Attribute Pattern & 830K & 90.25 \\ 
  Total Seen & 914K & --- \\ 
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in the NEW TYPE SYSTEM.}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:10:46 2019
\begin{table}[ht]
\label{tab:funcountsWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
 Function Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 143K & 66.02 \\ 
  Monomorphic in Type & 184K & 84.91 \\
%  Monomorphic in Class & 163K & 75.13 \\ 
%  Monomorphic in Attribute Pattern & 161K & 74.31 \\ 
  Total Seen & 216K & --- \\ 
   \hline
\end{tabular}
\caption{Account of {\it function} polymorphism in the NEW TYPE SYSTEM.}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Mar 26 17:46:45 2019
\begin{table}[ht]
\label{tab:toppolyWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
Polymorphic Type Signature & \# Occurrences & \% of Total Polymorphism \\ 
  \hline
  matrix, vector/real & 6320 & 13.25 \\ 
  list$<$any$>$, list$<$real$>$ & 2782 & 5.83 \\ 
  vector/character, vector/real & 2706 & 5.67 \\ 
  scalar/character, scalar/real & 2523 & 5.29 \\ 
  data.frame, matrix & 2163 & 4.53 \\ 
  list$<$any$>$, list$<$list$>$ & 1484 & 3.11 \\ 
  list$<$any$>$, list$<$character$>$ & 1211 & 2.54 \\ 
  data.frame, vector/real & 1027 & 2.15 \\ 
  scalar/logical, scalar/real & 911 & 1.91 \\ 
  scalar/character, vector/real & 839 & 1.76 \\ 
   \hline
\end{tabular}
\caption{Top 10 argument signatures in the NEW TYPE SYSTEM.}
\end{table}
